### 2016-07-03 paper/extended-example.tex
minified
added in space in BN def
moved
asdf
added in stuff

BNames = Name", " Name (" " (Name))*
Bib = ("" | ("author={" BNames (" and " BNames)* "},"))

ENames = Name (" " (Name))* (" " Name)
End = ("%A " ENames "\n")*

>>>>

BNames = Name ", " Name (" " Name)*
Bib = ""
    | "author={" BNames (" and " BNames)* "},"

ENames = Name (" " (Name))* " " Name
End = ("%A " ENames "\n")*
